Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-02-03 manuscript.tex
Updating dynamic model to define all variable

\todo{Add the schematic of dumbbell that you created for the dissertation?}

@@

Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
\begin{align}
    \dot{\vc{x}} &= \vc{v}, \\
    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2},\label{eq:v_dot} \\
    \dot{R} &= R S(\vc{\Omega}) , \\
    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2.
\end{align}
The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
\begin{align}
    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2}.
\end{align}
The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
\begin{align}
    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}
In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.

>>>>

@@

Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
\begin{align}
    \dot{\vc{x}} &= \vc{v}, \\
    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
    \dot{R} &= R S(\vc{\Omega}) , \\
    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m.
\end{align}
The vectors \( \vc{z}_1 \) and \( \vc{z}_2\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
\begin{align}
    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2},
\end{align}
where \( \rho_i \) defines the position of each mass in the spacecraft fixed body frame.
The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
\begin{align}
    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}
In the above equations, the gravitational potential is denoted by $U$, which is computed by a polyhedron model as described in the subsequent section.
